### 2017-12-12 submission/manuscript.Rmd
add results -- final section better edit

For all Taqs a positive correlation was observed between chimeric sequences and number of OTUs with this correlation being strongest for Platinum and Phusion HiFi Taq [Figure 5]. In general, the R^2^ value between the number of OTUs and chimeric sequences became stronger as sub-sampling depth increased [Figure 5]. Interestingly, Accuprime^TM^ not only had one of the lowest chimera prevalence but also consistently had the lowest correlations between the number of OTUs and chimeric sequences [Figure 5].

>>>>

For all Taqs a positive correlation was observed between chimeric sequences and number of OTUs, with this correlation being strongest for Platinum and Phusion HiFi Taq [Figure 5]. In general, the R^2^ value between the number of OTUs and chimeric sequences became stronger as sub-sampling depth increased [Figure 5]. Taken together this data suggests that a strong correlation exists between the number of OTUs and chimera sequence prevalence. Interestingly, Accuprime^TM^ not only had one of the lowest prevalence of chimeric sequences but also, consistently, had the lowest correlations between the number of OTUs and chimeric sequences across sub-sampling depth [Figure 5].

### 2017-12-12 submission/manuscript.tex
add results -- final section better edit

For all Taqs a positive correlation was observed between chimeric
sequences and number of OTUs with this correlation being strongest for
Platinum and Phusion HiFi Taq {[}Figure 5{]}. In general, the
R\textsuperscript{2} value between the number of OTUs and chimeric
sequences became stronger as sub-sampling depth increased {[}Figure
5{]}. Interestingly, Accuprime\textsuperscript{TM} not only had one of
the lowest chimera prevalence but also consistently had the lowest
correlations between the number of OTUs and chimeric sequences {[}Figure
5{]}.

>>>>

For all Taqs a positive correlation was observed between chimeric
sequences and number of OTUs, with this correlation being strongest for
Platinum and Phusion HiFi Taq {[}Figure 5{]}. In general, the
R\textsuperscript{2} value between the number of OTUs and chimeric
sequences became stronger as sub-sampling depth increased {[}Figure
5{]}. Taken together this data suggests that a strong correlation exists
between the number of OTUs and chimera sequence prevalence.
Interestingly, Accuprime\textsuperscript{TM} not only had one of the
lowest prevalence of chimeric sequences but also, consistently, had the
lowest correlations between the number of OTUs and chimeric sequences
across sub-sampling depth {[}Figure 5{]}.
